Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/type-theory.tex
Cosmetic changes.

We produce derivation trees inside the judgments using the derivation rules.
Since type theory can be seen as typed lambda calculus with dependent products,
evaluation of lambda terms also called \emph{normalization} of the proofs-terms, are reductions using the system inference rules.

Therefore, the task to verify a proof that proves a certain theorem is
translated to verify if the associated tree of the proof has the correspondent
type of the theorem. We know this process as \emph{type-checking}. This feature
of type theory allow us to verify a proof generated by \ATPs by reconstructing
its proof-term to type-check the proof. For such a purpose, we use a proof
assistant in type theory like \Agda to delegate this task.  However, this
approach has some weak points discussed in~\cite{Bezem2002}. Some limitations
from the type theory point of view for proof-reconstruction is described in the
following section.

>>>>

We produce derivation trees inside the judgments using the derivation
rules.  Since type theory can be seen as typed $λ$-calculus with
dependent products, evaluation of $λ$-terms also called
\emph{normalization} of the proof-terms, are reductions using the
system inference rules.

Therefore, the task to verify a proof that proves a certain theorem is
translated to verify if the associated tree of the proof has the
correspondent type of the theorem. We know this process as
\emph{type-checking}. This feature of type theory allow us to verify a
proof generated by an \ATP by reconstructing its proof-term to
type-check the proof. For such a purpose, we use a proof assistant in
type theory like \Agda to delegate this task.  However, this approach
has some weak points discussed in~\cite{Bezem2002}. Some limitations
from the type theory point of view for proof-reconstruction is
described in the following sections.
